PS753 Glossary

### 2022-02-01 _academics/ps753-glossary/ps753-glossary.Rmd
update geodesic distance definition

geodesic distance
: the shortest path between two nodes; by definition, not a trail or walk because repeated segments wouldn't be the shortest; with binary data, the number of steps; with weighted data, might be a sum or some other calculation of "effort"

>>>>

geodesic distance
: the shortest path between two nodes; by definition, not a trail or walk because repeated segments wouldn't be the shortest; with binary data, the number of edges between the nodes; with weighted data, might be a sum or some other calculation of "effort"
